On the presentation of orthogonal groups over polynomial rings

### 2019-01-15 dl-paper.tex
Added couple of lemmas

\theoremstyle{definition}
\newtheorem{df}[lemma]{Definition} \Crefname{df}{Definition}{Definitions}
\newtheorem{example}[lemma]{Example} \Crefname{example}{Example}{Examples}
\newtheorem{rem}[lemma]{Remark}
\DeclareMathOperator{\St}{St}
\DeclareMathOperator{\K}{K}
\DeclareMathOperator{\GW}{GW}
\DeclareMathOperator{\colim}{colim}
\newcommand{\XX}{\mathcal{X}}           % (subset of) Steinberg generators
\newcommand{\RR}[1]{\mathcal{R}_{#1}}   % Steinberg relations
\newcommand{\rA}{\mathsf{A}}
\newcommand{\rB}{\mathsf{B}}
\newcommand{\rC}{\mathsf{C}}
\newcommand{\rD}{\mathsf{D}}
\newcommand{\rE}{\mathsf{E}}
\newcommand{\rF}{\mathsf{F}}
\newcommand{\rG}{\mathsf{G}}

@@

\subsection{Relative Steinberg groups}
% Generation of relative Steinberg groups

@@

\begin{lemma}
 For a field $F$ and $\ell \geq 5$ the canonical map $\K_3(\rD_\ell, F[X]) \to \K_3(\rD_\ell, F[X^{\pm 1}])$ is surjective.
\end{lemma}
\begin{proof}
 We have defined $\K_3(\rD_\ell, R)$ as 
\end{proof}

\subsection{Second injectivity theorem}

\begin{comment}
\[x_{\alpha}(aX^{-1}) x_{-\alpha}(mX) x_{\alpha}(-a(1+am)^{-1}X^{-1}) \cdot \{X, 1+am\} \in G_+.\]
$y := x_{\alpha}(aX^{-1}) x_{-\alpha}(mX) x_{\alpha}(-a(1+am)^{-1}X^{-1})$, 
$z = x_{-\alpha}(-m(1+am)^{-1}X) y h_{\alpha}((1+am)^{-1})$,
Using $\pi(z) = 1$ we get 
\begin{multline}z = z^{h_{ik}^{-1}(X)} = \\ x_{ji}(-m(1+am)^{-1}) x_{ij}(a) x_{ji}(m) \cdot x_{ij}(-a(1+am)^{-1})\{X, (1+am)^{-1}\} \cdot h_{ij}((1+am)^{-1}) \in G. \end{multline}
\end{comment}

>>>>

\theoremstyle{definition}
\newtheorem{df}[lemma]{Definition} \Crefname{df}{Definition}{Definitions}
\newtheorem{example}[lemma]{Example} \Crefname{example}{Example}{Examples}
\newtheorem{rem}[lemma]{Remark}
\DeclareMathOperator{\St}{St}
\DeclareMathOperator{\G}{G}
\DeclareMathOperator{\E}{E}
\DeclareMathOperator{\HH}{H}
\DeclareMathOperator{\K}{K}
\DeclareMathOperator{\GW}{GW}
\DeclareMathOperator{\colim}{colim}
\newcommand{\XX}{\mathcal{X}}           % (subset of) Steinberg generators
\newcommand{\RR}[1]{\mathcal{R}_{#1}}   % Steinberg relations

\newcommand{\ZZ}{\mathbb{Z}}
\newcommand{\rA}{\mathsf{A}}
\newcommand{\rB}{\mathsf{B}}
\newcommand{\rC}{\mathsf{C}}
\newcommand{\rD}{\mathsf{D}}
\newcommand{\rE}{\mathsf{E}}
\newcommand{\rF}{\mathsf{F}}
\newcommand{\rG}{\mathsf{G}}

@@

\subsection{Relative Steinberg groups}
% Generation of relative Steinberg groups
Let us briefly remind the reader definitions and basic properties pertaining to relative Steinberg groups.
We refer the reader to~\cite[Section~3]{S15} for a more detailed exposition.
%TODO: Define the category of pairs (so that all constructions below become functorial wrt it).

Thus, by our definition, the relative Steinberg group is a central extension of $\St(\Phi, R)$.
\begin{equation}\label{eq:relative-St}
 \xymatrix{ 1 \ar[r] & C(\Phi, R, I) \ar[r] & \St(\Phi, R, I) \ar[r] & \St(\Phi, R) \ar[r]^{\pi^*} & \St(\Phi, R/I) \ar[r] & 1 }
\end{equation}
It is not hard to show that $C(\Phi, R, I) = 0$ in the case when $I$ is a splitting ideal of $R$, i.\,e. when the canonical map $R \to R/I$ splits, see~\cite[Lemma~8]{S15}. In order to better understand $C(\Phi, R, I)$  we would like to continue the sequence~\eqref{eq:relative-St} to the left. Thus we need to work with unstable $\K_3$-functors for which we choose the definition a la Quillen (cf.~\cite{Pa89})

\begin{df} Suppose that $\St(\Phi, R)$ is perfect and super-perfect (i.\,e. the homology groups $\HH_i(\St(\Phi, R), \ZZ)$ vanish for $i=1,2$.) Denote by $X$ the result of application of Quillen's $+$-construction to the discrete classifying space $B\G(\Phi, R)$ with respect to the elementary subgroup $\E(\Phi, R)$. Now define $\K_3(\Phi, R)$ as the third homotopy group $\pi_3(X)$. \end{df}
%TODO: Give reference on the definition of the plus-construction?

\begin{prop} The group $\K_3(\Phi, R)$ is isomorphic to $\HH_3(\St(\Phi, R), \ZZ)$. In particular, it does not depend on the isogeny form of $\G(\Phi, R)$ used to define it. Moreover, for a ring epimorphism $R \to R/I$ there is a functorial exact sequence
\[ \xymatrix{\K_3(\Phi, R) \ar[r] & \K_3(\Phi, R/I) \ar@{->>}[r] & C(\Phi, R, I).} \]
\end{prop}

\begin{lemma} \label{lem:Panin-stability}
 Let $R$ be either a field, principal ideal domain or a Dedekind domain. 
 Then the canonical map $\K_3(\rD_\ell, R) \to \K_3(\rD_\infty, R)$ is an epimorphism for $\ell \geq 6$ 
 and an isomorphism for $\ell \geq 7$.
\end{lemma}
\begin{proof}
 Stabilization for orthogonal and symplectic K-groups a la Quillen is given by Panin's theorem, see~\cite[Theorem~9.4]{Pa89}. More specifically the bounds for surjective (resp. injective) stability is 
 $\ell \geq \max(6, a+2)$ (resp. $\ell \geq \max(7,a+3)$) for $a=1,2,3$ in the case when $R$ is a field, p.i.d. or a Dedekind domain, respectively.
\end{proof}

@@

\begin{lemma}
 Let $F$ be a field of characteristic $\neq 2$. Then for $\ell \geq 7$ the canonical map $\K_3(\rD_\ell, F[X]) \to \K_3(\rD_\ell, F[X^{\pm 1}])$ is surjective.
\end{lemma}
\begin{proof}
 We have defined $\K_3(\rD_\ell, R)$ as 
\end{proof}

\subsection{Second injectivity theorem}
\begin{comment}
\[x_{\alpha}(aX^{-1}) x_{-\alpha}(mX) x_{\alpha}(-a(1+am)^{-1}X^{-1}) \cdot \{X, 1+am\} \in G_+.\]
$y := x_{\alpha}(aX^{-1}) x_{-\alpha}(mX) x_{\alpha}(-a(1+am)^{-1}X^{-1})$, 
$z = x_{-\alpha}(-m(1+am)^{-1}X) y h_{\alpha}((1+am)^{-1})$,
Using $\pi(z) = 1$ we get 
\begin{multline}z = z^{h_{ik}^{-1}(X)} = \\ x_{ji}(-m(1+am)^{-1}) x_{ij}(a) x_{ji}(m) \cdot x_{ij}(-a(1+am)^{-1})\{X, (1+am)^{-1}\} \cdot h_{ij}((1+am)^{-1}) \in G. \end{multline}
\end{comment}
